More than space for time: revealing the tight links constraining the temporal dynamics of network structure

### 2021-05-27 paper/manuscript.Rmd
Fix results

---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

theme_set(mytheme)
```

@@

@@

We described community structure by its total biomass, species richness and the
evenness of the number of individual and the amount of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species).

@@

```{r}
loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
rsq <- summary_table %>%
  filter(y %in% get_com_str_var(all = FALSE), x %in% c("log_bm_std",
      "log_rich_std")) %>%
select(y, x, mod_summary_table) %>%
unnest(mod_summary_table) %>%
select(y, x, r.squared, adj.r.squared)
```

@@

### Food-web structure and biomass

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
reg_bm <- model_log_bm_f3y_table_medium$reg_table
#reg_bm[reg_bm$y == ]
```
We found a significant positive relationship between the temporal trends of total biomass from
one side and species richness, average trophic level, connectance from the other
side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)), meaning that they increased in time when
the total biomass increased in time and respectively that they decreased in time
when the total biomass decreased in time.

We found that a significant negative relationship between the temporal trends of
total biomass and that of the pielou of biomass (slopes XX, Figure X, Table X),
meaning that the eveness of biomass across species increased in time when the
total biomass decreased in time and respectively that the evenness decreased
in time when the total biomass increase in time (Fig. \@ref(fig:bm), Table
\@ref(tab:aov-bm)). However, we found no relationship between the temporal
trends of total biomass and that of the pielou
of individual.

@@

The temporal trends of total biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species richness
(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
relationship between the temporal trends of average trophic level and the one of
species richness was not significant after controling for total biomass temporal
trends.

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Figure X, Table X). The relationship
between temporal trends of pielou of individual and that of species richness was
more positive as the community contained more species (+ XX by species by square
meter). While the relationship between temporal trends of pielou of individual
and that of species richness was more negative as the community contained more
species.

@@

@@

The temporal dynamic of the species richness was positively linked to that of
biomass. In non-temporal data, this result was already found in streams
[@woods_testing_2020; @danet_species_nodate] but also in grasslands salt marches
and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@wu_relationship_2015; @li_relationship_2018; but see @grace_integrative_2016]. Therefore,
our results confirm BEF prediction works also in time.

*From the previous manuscript*: the positive relationship of species richness on total
biomass might be due to resource use complementarity [@carey_determining_2011],
which is held by niche differentiation [@loreau_biodiversity_1998;
@loreau_partitioning_2001] or to the higher probability of getting high biomass
species with higher species richness [@loreau_biodiversity_2001].

We found the temporal dynamic of connectance was negative associated, but
weakly, with that one of species richness as found in most empirical foodweb
[@dunne_network_2006]. The relationship is very weak in species rich commuties
and more negative for species poor commuties. An explanation might be that
species-rich communities already contains a significant number of piscivores, which have the
most links whereas species poor communites contains few piscivores.

The temporal dynamic of the average trophic level had no relationship with the
one of species richness. It is surprising because one can imagine that loss and
gain of species would reveal assembly/disassembly mechanisms in terms of trophic
structure. However, we found that when species richness increases, the
distribution of biomass and individuals among species become more even in the
community, meaning that dominance decrease. Species richness has often been
found to be positively or negatively related to individual eveness
[@soininen_relationship_2012; @maureaud_biodiversity_2019].

We further found that the temporal dynamic of the average trophic level was positively
linked to that of biomass. Increase  of average trophic level can be associated
to either gain of biomass in the highest trophic level nor losses of biomass in
the lowest trophic. In our case, such gain or losses of average trophic level is
certainly associated to the loss or the gain of the biggest individuals. Because
it seems unlikely that a community gain or loss biomass while respectively
losing or gaining individuals. Pielou index temporal dynamics further confirm
this interpretation.

We found that the pielou of biomass decrease through time
as total biomass decrease and reversely, meaning that biomass distribution
across species respectively became less and more even when total biomass
decrease and increase. The structuration in size class of the community might
explain this pattern.

Finally, we found no relationship between the temporal
dynamics of pielou based on indivual number and that one of biomass, confirming
that the temporal trends of total biomass in our study is linked to few big
individuals. @maureaud_biodiversity_2019 found negative relationship between
biomass and eveness of indivual in marine ecosystem. One explanation is that
marine ecosystem studied in [@maureaud_biodiversity_2019] are much larger than
the stream communities studied in this study.

We further found that the temporal dynamic of connectance was positively
linked to that one of total biomass, meaning that connectance increases through
time in a given site when total biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This is because the predation window of
freshwater fish species is highly nested.

Our results indicate that biomass trends are linked to few big individuals while
richness trends are linked to overall shift in dominance in communities. This
results has profound implications for conservation. As more and more studies
report biomass and richness temporal dynamics [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further
studies should investigate several dimensions of community structure because it
drives many aspects of ecosystem functioning.

@@

We found that total biomass was linked positively related to species richness
both in space and in time, indicating that space for time might be use. In the
same way, we found a positive positive relationship between average trophic
level and total biomass both in time and in space. However, it was not the case
for connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. Moreover, connectance displayed a strong positive
relationship (move to results?) with biomass in time but not in space.

@@

```{r}
loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
theme_set(theme_cowplot())
p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
  bm_x = "bm_std", rich_x = "rich_std"
  )$bm
plot_grid(plotlist = p_bm)

sp_bm <- sp_relation_plot2 %>%
  filter(x == "bm_std")
p_sp_bm <- sp_bm$gg 
names(p_sp_bm) <- sp_bm$y

@@

```{r}
fig1_left <- plot_grid(plotlist = p_bm, ncol = 1)
fig1_right <- plot_grid(plotlist = p_sp_bm, ncol = 1)
#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

ti <- list()
for (i in 1:5) {
  ti[[i]] <- list(p_bm[[i]], reorder_p_sp_bm[[i]]) 
}

```{r bm, fig.height = 12}
# Make the label on two lines 
top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1)) 
fig1
```

```{r}
p_rich <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE)$rich
#plot_grid(plotlist = p_rich)

sp_rich <- sp_relation_plot2 %>%
  filter(x == "log_rich_std")
p_sp_rich <- sp_rich$gg
names(p_sp_rich) <- sp_rich$y

reorder_p_sp_rich <- p_sp_rich
reorder_p_sp_rich[[1]] <- p_sp_rich$ct_ff 
reorder_p_sp_rich[[2]] <- p_sp_rich$w_trph_lvl_avg 
reorder_p_sp_rich[[3]] <- p_sp_rich$piel_nind 
reorder_p_sp_rich[[4]] <- p_sp_rich$piel_bm 
reorder_p_sp_rich[[5]] <- p_sp_rich$log_bm_std

@@

trich <- list()
for (i in 1:5) {
  trich[[i]] <- list(p_rich[[i]], reorder_p_sp_rich[[i]]) 
}
```

```{r rich, fig.height = 12}
# Make the label on two lines 
top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

```{r}
```

# Tables

@@

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of 
      community biomass and the temporal trends of the network structure."
    ),
  label = "tab:aov-bm"

@@

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "tab:aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "tab:reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>% 
  filter(y %in% get_com_str_var(all = FALSE)) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "tab:reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
tab_sp_anova$log_bm_std %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "tab:aov-bm-sp"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "tab:aov-rich-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}

table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
  ~mutate(.x, Explicative = .y) %>%
    select(Explicative, Response, Marginal, Conditional)
) %>%
do.call(rbind, .)

table_rsq_sp %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "tab:rsq-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")

>>>>

---
title: "More than space for time: revealing the tight links constraining the temporal dynamics of network structure"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
fontsize: 12pt
output:
  bookdown::html_document2:
    fig_caption: true
    theme: "journal"
---

@@

theme_set(mytheme)
bookdown::html_document2
library(bookdown)
```
```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

@@

We selected the stations that have been monitored at least 10 times on the
1995-2018 period.

@@

We described community structure by its community biomass, species richness and the
evenness of the number of individual and the amount of biomass across species. The evenness was
quantified with the Pielou index, computed as the Shannon diversity index
divided by the number of species ($P = \frac{H'}{N}$, with $H'$ being the
Shannon diversity index and $N$ the number of species).

@@

```{r}
loadd(rsq_sp_mod, summary_table, sp_models, model_summary)
rsq <- summary_table %>%
  filter(y %in% unique(c(net_var_bm, net_var_rich))) %>%
select(y, x, mod_summary_table) %>%
unnest(mod_summary_table) %>%
select(y, x, r.squared, adj.r.squared)
```

@@

### Community structure and community biomass

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
reg_bm <- model_log_bm_f3y_table_medium$reg_table
#reg_bm[reg_bm$y == ]
```
We found a significant positive relationship between the temporal trends of
community biomass from one side and species richness, average trophic level,
connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)),
meaning that they temporally increased when the community biomass temporally increased and
respectively that they temporally decreased when the community biomass decreased in
time.

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
\@ref(tab:aov-bm)), meaning that the eveness of biomass across species
temporally increased when the community biomass temporally decreased and
respectively that the evenness temporally decreased when the community biomass
temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov-bm)). However, we
found no significant relationship between the temporal trends of community biomass and that
of the pielou of individual.

Overall, we did not find effect of assembly/disassembly on the relationships
between the temporal trends of community structure and the one of community
biomass. We also found that the median community biomass had no effect on the
relationship between the temporal trends of community structure and the one of community
biomass.

@@

The temporal trends of community biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species richness
(Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich)). However, the direct
relationship between the temporal trends of average trophic level and the one of
species richness was not significant after controling for community biomass temporal
trends [**TO CHECK: refaire tous les modèles temporels en mettant à la fois la
pente des biomasses et de la richness en même temps??**].

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Fig. \@ref(fig:rich), Table
\@ref(tab:aov-rich)), meaning that the relationship between temporal trends of
pielou of individual and that of species richness was more positive as the
community contained more species (Fig. \@ref(fig:rich), Table
\@ref(tab:reg-rich)). While the relationship between temporal trends of pielou
of individual and that of species richness was more negative as the community
contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg-rich)).

## Spatial relationships

### Community structure and community biomass

We found that species richness, connectance, average trophic level were
spatially positively related to community biomass while the pielou of biomass was negatively related to
community biomass (Fig. \@ref(fig:bm), Table \@ref(tab:aov-rich-sp)). However,
we found no spatial relation between the pielou of individual and community
biomass.

We found that community biomass, the pielou of biomass and individual were
positively related to species richness while average trophic level and
connectance were negatively related to
community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-rich-sp)).

@@

We found that the temporal increase of the average trophic level was positively
linked to increase of community biomass. Increase of average trophic level can
be associated to either gain of biomass in the highest trophic level nor losses
of biomass in the lowest trophic. In our case, such gain or losses of average
trophic level is probably associated to the variations of the presence of large
fishes. This interpretation is confirmed by the finding that the evenness of
biomass, measured by the pielou, decreased through time as community biomass
decrease and reversely, meaning that biomass distribution across species
respectively become respectively less and more even when community biomass
decrease and increase. We also found no relationship between the temporal trends of evenness based
on indivual number and that community biomass, confirming that the temporal trends
of community biomass in our study is linked to few big individuals. It further
indicates that temporal loss of community biomass are linked with the loss of
the higher trophic level.

We also found in space that evenness of biomass was positively related to
community while eveness of individual number had no relation. It constrasts with
previous studies which found a negative relationship between biomass and eveness
of individual in marine and plant communities [@drobner_relation_1998;
@maureaud_biodiversityecosystem_2019] or studies that found more even plant
communities in terms of individual number display higher community biomass
[@wisley_biodiversity_2000].

We further found that the temporal trends of connectance was positively
linked to that one of community biomass, meaning that connectance increases through
time in a given site when community biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This result is also in accordance with  
theoretical work showing that higher food-web connectance result in higher
community biomass [@thebaut_food-web_2003].

To the difference with community biomass, the temporal trends evenness of
biomass and individual were positively related to the temporal trends of species
richness, meaning that as community biomass temporally increase, the
distribution of biomass and abondance become more even. Our results indicate
that biomass trends are linked to few big individuals while richness trends are
linked to overall shift in dominance in communities.

Surprinsingly, we found the temporal trends of connectance was not related to
the one of species richness as found spatially in most empirical foodweb
[@dunne_network_2006]. However, the relationship become slightly negative for
species poor communities. An explanation might be that species-rich communities
already contains a significant number of piscivores, which have the most links
whereas species poor communites contains few piscivores.

@@

Spatially and temporally, the species richness was positively linked to that of
biomass. Spatially, this result is in accordance with numerous studies was
already found in streams [@woods_testing_2020; @danet_species_nodate] but also
in grasslands, salt marches and forests [@hector_plant_1999;
@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018; but see
@grace_integrative_2016]. Therefore, our results confirm that BEF prediction
works also in time. The positive relationship of species richness on total
biomass might be due to resource use complementarity [@carey_determining_2011],
which is held by niche differentiation [@loreau_biodiversity_1998;
@loreau_partitioning_2001] or to the higher probability of getting high biomass
species with higher species richness [@loreau_biodiversity_2001].

HERE
 @soininen_relationship_2012;

The temporal trend of the average trophic level had no relationship with the
one of species richness. It is surprising because one can imagine that loss and
gain of species would reveal assembly/disassembly mechanisms in terms of trophic
structure. However, we found that when species richness increases, the
distribution of biomass and individuals among species become more even in the
community, meaning that dominance decrease. Species richness has often been
found to be positively or negatively related to individual eveness
[ @maureaud_biodiversityecosystem_2019].

We found that community biomass was linked positively related to species richness
both in space and in time, indicating that space for time might be use. In the
same way, we found a positive positive relationship between average trophic
level and community biomass both in time and in space. However, it was not the case
for connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. Moreover, connectance displayed a strong positive
relationship (move to results?) with biomass in time but not in space.

This result has profound implications for conservation. As more and more
studies report community biomass and richness trends [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further
studies should investigate the temporal trends of several dimensions of
community structure simultaneously because it drives many aspects of ecosystem functioning.

@@

@@

```{r}
fig_bm_cap <- paste0(
  "Relationship between community structure and community biomass. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of community biomass. Lines correspond to the predictions of the
  linear models while the points are colored according the median community
  biomass of the three first years of the given temporal series. The lines surrounding each point represent
  the standard error associated to the temporal trends. Right panel displays the
  spatial relationship between median community structure over time and the
  median community biomass over time."

)

fig_rich_cap <- paste0(
  "Relationship between community structure and species richness. Left panel
  displays the relationships between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models while the points are colored according the median species
  richness of the three first years of the given temporal series. The lines
  surrounding each point represent the standard error associated to the temporal
  trends. Right panel displays the spatial relationship between median community
  structure over time and the median species richness over time."

)
```

```{r}
loadd(p_fig1_2, sp_relation_plot2, predict_plot2)
theme_set(theme_cowplot())
p_bm <- get_plot_fig1_2(predict_plot = predict_plot2, get_list = TRUE,
  bm_x = "log_bm_std", rich_x = "log_rich_std",
  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_rich_std") 
  )$bm
names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "piel_nind",
  "piel_bm") 
#plot_grid(plotlist = p_bm)

sp_bm <- sp_relation_plot2 %>%
  filter(x == "log_bm_std")
p_sp_bm <- sp_bm$gg 
names(p_sp_bm) <- sp_bm$y

@@

```{r}
ti <- list()
for (i in c("log_rich_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]]) 
}
```

```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
# Make the label on two lines 
top <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1 <- plot_grid(top, p_bm[[6]], ncol = 1, rel_heights = c(1, .1)) 
fig1
```

```{r}
p_rich <- get_plot_fig1_2(
  predict_plot = predict_plot2,
  get_list = TRUE,
  rich_x = "log_rich_std",
  rich_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std") 
  )$rich
names(p_rich) <- c(
  "ct_ff", "w_trph_lvl_avg", "piel_nind",
  "piel_bm", "log_bm_std")
#plot_grid(plotlist = p_rich)

sp_rich <- sp_relation_plot2 %>%
  filter(x == "log_rich_std")
p_sp_rich <- sp_rich$gg
names(p_sp_rich) <- sp_rich$y
```

@@

trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]]) 
}
```

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines 
top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

# Tables {-}

@@

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_bm) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of 
      community biomass and the temporal trends of the network structure."
    ),
  label = "tab:aov-bm"

@@

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_rich) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "tab:aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% net_var_bm) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "tab:reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>%
  filter(y %in% net_var_rich) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "tab:reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
tab_sp_anova$log_bm_std %>%
  filter(y %in% net_var_bm) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "tab:aov-bm-sp"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  filter(y %in% net_var_rich) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "tab:aov-rich-sp"
      ) %>% # 
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
table_rsq_sp <- map2(rsq_sp_mod, names(rsq_sp_mod),
  ~mutate(.x, Explicative = .y) %>%
    select(Explicative, Response, Marginal, Conditional)
) %>%
do.call(rbind, .)
rownames(table_rsq_sp) <- NULL

table_rsq_sp %>%
  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "tab:rsq-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
